TUDatasets: A collection of benchmark datasets for learning with graphs

### 2020-04-26 main.tex
MC
dmkljdw
Added max iterations to linear svm.

\twocolumn[
\icmltitle{TUD Datasets: A collection of benchmark datasets for learning with graphs}
\icmlsetsymbol{equal}{*}

@@

\begin{table*}[t]\centering		
	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
	\label{t2l}	
	\resizebox{0.6\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule

			& \multirow{3}{*}{\vspace*{4pt}\textbf{Graph Kernel}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
			& & {\textsc{Data0}}         &  {\textsc{Data1}}      & {\textsc{Data1}}           & {\textsc{Data1}}       & {\textsc{Data1}}           & {\textsc{Data1}}      \\	\toprule
			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
				& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
				& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
				& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
			\cmidrule{2-8}	
			\multirow{4}{*}{\rotatebox{90}{GNN}}	& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
		& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
		& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
		& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
			\bottomrule
	\end{tabular}}
\end{table*}

>>>>

\twocolumn[
\icmltitle{TUDatasets: A collection of benchmark datasets for learning with graphs}
\icmlsetsymbol{equal}{*}

@@

\begin{table*}[t]\centering		
	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
	\label{t2l}	
	\resizebox{0.8\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule

			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}     \\	\toprule
			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &  50.1  \scriptsize $\pm 1.6 \pm 6.2 $       & 72.4 \scriptsize $\pm  0.5 \pm 4.0$ & 50.1  \scriptsize $\pm 0.5 \pm  3.8 $ & 84.3 \scriptsize $\pm 0.3 \pm 1.6$ &73.0  \scriptsize $\pm 0.8 \pm  4.2 $ & 72.6 \scriptsize $\pm  0.4 \pm 3.1$  \\
				& \text{WLOA} & 56.8  \scriptsize $\pm  1.7\pm6.4 $       & 72.7  \scriptsize $\pm 0.7 \pm 4.3$ & 49.5 \scriptsize $\pm  0.4 \pm  3.5 $ & 84.9 \scriptsize $\pm  0.4 \pm 1.7$ &73.4  \scriptsize $\pm 0.7 \pm 3.7$ & 88.1 \scriptsize $\pm 0.3 \pm 2.5 $   \\
				& \text{GR}            &  31.9   \scriptsize $\pm 1.1 \pm4.8$       & 59.4  \scriptsize $\pm 0.4 \pm 4.6$ & 39.3 \scriptsize $\pm 0.8 \pm  4.1 $ & 58.7  \scriptsize $\pm 0.4 \pm 2.3$ & 69.0  \scriptsize $\pm 0.8 \pm 4.3$ &60.0  \scriptsize $\pm 0.2 \pm 3.2 $   \\
				& \text{SP}            &  40.6 \scriptsize $\pm  1.8\pm 5.8 $       & 58.3  \scriptsize $\pm 0.8 \pm  4.9$ & 39.0 \scriptsize $\pm 0.5 \pm  3.8$ &  74.1  \scriptsize $\pm 0.5 \pm 2.0 $  & 75.4  \scriptsize $\pm 0.5 \pm 4.1$ & 84.6 \scriptsize $\pm 0.3 \pm 2.5 $  \\
			\cmidrule{2-8}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GIN-$\varepsilon$}    &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $    \\
		& \text{Sage}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $  \\
			\bottomrule
	\end{tabular}}
\end{table*}

\begin{table*}[t]\centering		
	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
	\label{t2l}	
	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Triangles}}           & {\textsc{github\_stargazers}}       & {\textsc{reddit\_threads}}      \\	\toprule
							\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 94.23 
							   \scriptsize $\pm 0.11  \pm 0.49$       & 94.29 \scriptsize $\pm 0.07  \pm 0.39$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\

			& \text{GR}            &  91.71 \scriptsize $\pm  0.04   \pm 0.52 $       & 92.10  \scriptsize $\pm 0.02 \pm 0.45$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\  
			& \text{SP}             &   91.73 \scriptsize $\pm 0.03  \pm 0.49$       & 92.05 \scriptsize $\pm 0.02 \pm 0.44 $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\   
			\cmidrule{2-7}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GIN-E-$\varepsilon$}         &    \scriptsize $\pm  \pm $       & \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ \\
			& \text{Sage}            &    \scriptsize $\pm \pm$       & \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm $  \\
			\bottomrule
	\end{tabular}}
\end{table*}

\begin{table}[t]\centering		
	\caption{Results for neural and kernel baselines.}
	\label{t2l}	
	\resizebox{0.55\columnwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
		\begin{tabular}{@{}c <{\enspace}@{}lcc@{}}	\toprule

			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{2}{c}{\textbf{Dataset}}\\\cmidrule{3-4}
			&  & {\textsc{Zinc} (10k)}         &  {\textsc{Zinc} (50k)}         \\	
			\toprule
			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}             &      \scriptsize $<\!0.000$ &  \scriptsize $ <\!0.000$  \\  
				& \text{GR}            &\scriptsize $ <\!0.000$ &  \scriptsize $ <\!0.000$  \\  
			& \text{SP}             &   \scriptsize $ <\!0.000$  &  \scriptsize $ <\!0.000$ \\   
			\cmidrule{2-4}
			\multirow{2}{*}{\rotatebox{90}{GNN}} & \text{$1$-GNN-E}             &  0.278 \scriptsize $\pm 0.022$  & 0.145 \scriptsize $\pm  0.006  $		\\	
			& \text{$1$-GNN}             &  0.383 \scriptsize $\pm  0.020$    &  0.247 \scriptsize $\pm   0.020$ \\
			\bottomrule
	\end{tabular}}
\end{table}
